Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2020-03-25 Scripts/Initial_Analysis.Rmd
add time just for controling
added parallelization

#### Library ####
packages <- c(
  "tidyverse",
  "here", # for dbem_import `here()`
  "data.table", #dbem_import `fread()`
  "readxl", # for reading excell files
  "janitor", # for clearing names
  "geosphere", # estimate distances between points `distm()`
  "ggrepel",
  "zoo"
)

@@

lapply(
  spp_list, #c(600004,600005),
  EstPropChange,
  year <- year_df,
  data_type <- "Catch",
  ensamble_list = ensamble_list,
  path = DBEM_path,
  neighbours = Neighbours
)

>>>>

#### Library ####
packages <- c(
  "tidyverse",
  "here", # for dbem_import `here()`
  "data.table", #dbem_import `fread()`
  "readxl", # for reading excell files
  "janitor", # for clearing names
  "geosphere", # estimate distances between points `distm()`
  "ggrepel",
  "zoo",
  "parallel" # for mclapply
)

@@

t_start <- Sys.time()

mclapply(
  spp_list, #c(600004,600005),
  EstPropChange,
  year <- year_df,
  data_type <- "Catch",
  ensamble_list = ensamble_list,
  path = DBEM_path,
  neighbours = Neighbours
)

t_end <- Sys.time()-t_start;t_end
